---
title: "p8105_hw6_yy3563"
author: "Yifei Yu"
date: "2024-11-20"
output: github_document
---

```{r}
library(tidyverse)
library(broom)
library(modelr)
```

## Problem 1

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
set.seed(123)
boot_sample = function(df) {
  
  boot_df = 
    sample_frac(df, replace = TRUE) 
  
  return(boot_df)
  
  }
boot_straps =
  tibble(
    strap_number = 1:5000
  ) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(df = weather_df)),
    models = map(strap_sample, \(strap_df) lm(tmax ~ tmin, data = strap_df)),
    results = map(models, broom::tidy),
    results2 = map(models, broom::glance)
  )

boot_results =
  boot_straps |> 
  select(strap_number, results, results2) |> 
  unnest(results2) |> 
  select(strap_number, r.squared, results) |> 
  unnest(results) |> 
  group_by(strap_number, r.squared) |> 
  summarize(logbeta=log(prod(estimate)), .groups="drop")
```


```{r}
boot_results |> 
  ggplot(aes(x = r.squared)) + 
  geom_histogram()
```


```{r}
boot_results |> 
  ggplot(aes(x = logbeta)) +
  geom_histogram()
```

Both distributions are approximate normal. These distributions indicate a reliable linear relationship between `tmin` and `tmax`, both in terms of explained variance and the model coefficients.

```{r}
boot_results |> 
  summarize(
    boot_est = mean(r.squared),
    boot_se = sd(r.squared),
    boot_ci_ll = quantile(r.squared, 0.025),
    boot_ci_ul = quantile(r.squared, 0.975)
  )
```

The 95% confidence interval for the $r^2$ is (0.895,	0.927).

```{r}
boot_results |> 
  summarize(
    boot_est = mean(logbeta),
    boot_se = sd(logbeta),
    boot_ci_ll = quantile(logbeta, 0.025),
    boot_ci_ul = quantile(logbeta, 0.975)
  )
```

The 95% confidence interval for the $log(\hat{\beta_0}\cdot\hat{\beta}_1)$ is (1.96,	2.06).


## Problem 2 (The codes actually work, but need a lot of time to run. I'm sorry.)

```{r}
data = read_csv("data/homicide-data.csv")
data = data |> 
  mutate(city_state=paste0(city, ", ", state)) |> 
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", 
                            "Kansas city, MO",
                           "Tulsa, AL")) |> 
  filter(victim_race %in% c("Black", "White")) |> 

   mutate(solved = ifelse(disposition == "Closed by arrest", 1, 0)) |> 
  filter(!is.na(victim_age), 
         !is.na(solved),
         !is.na(victim_sex),
         !is.na(victim_race)
         )
```

```{r}
library(broom)
model1 = glm(solved ~ victim_age + victim_sex + victim_race, 
              subset(data, city_state == "Baltimore, MD"),
              family="binomial")
tidy_model = tidy(model1, conf.int = TRUE)
tidy_model |> 
  filter(term == "victim_sexMale") |> 
  mutate(oddsratio = exp(estimate),
         lower = exp(conf.low),
         upper = exp(conf.high)) |> 
  select(estimate, oddsratio, lower, upper)
```

The adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed is 0.456, the 95% Confidence Interval for the Adjusted Odds Ratio is (0.339, 0.612).

```{r}
extract_odds_ratio = function(city_data) {
  model = glm(solved ~ victim_age + victim_sex + victim_race,
               data = city_data,
               family = "binomial")

  tidy_model = tidy(model, conf.int=T)
  sex_coef = tidy_model |> 
    filter(term == "victim_sexMale")
  
  odds_ratio = exp(sex_coef$estimate)
  ci_lower = exp(sex_coef$conf.low)
  ci_upper = exp(sex_coef$conf.high)

  tibble(
    city = unique(city_data$city_state),
    odds_ratio = odds_ratio,
    ci_lower = ci_lower,
    ci_upper = ci_upper
  )
}

results = data |> 
  group_by(city_state) |> 
  nest() |> 
  mutate(odds_ratio_data = map(data, extract_odds_ratio)) |> 
  select(city_state, odds_ratio_data) |> 
  unnest(odds_ratio_data)
head(results)
```


```{r}
results |> 
  ggplot(aes(x = reorder(city_state, odds_ratio), 
                    y = odds_ratio)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_point() +
  coord_flip() +  
  labs(x = "City", 
       y = "Estimated Odds Ratio (OR)", 
       title = "Estimated Odds Ratios and 95% Confidence Intervals") +
  theme_minimal() + 
  theme() 
```

Most cities have odds ratios near or slightly above 1, suggesting that, in general, male victims are somewhat more likely to have their cases solved compared to female victims.


## Problem 3

```{r}
birthweight = read_csv("data/birthweight.csv")

birthweight = 
  birthweight |> 
  mutate(
    babysex = factor(babysex, levels = 1:2, labels = c("Male", "Female")),
    frace = factor(frace, levels = c(1, 2, 3, 4, 8),
                   labels = c("White", "Black", "Asian", "Puerto Rican", "Other")),
    mrace = factor(mrace, levels = c(1, 2, 3, 4, 8),
                   labels = c("White", "Black", "Asian", "Puerto Rican", "Other"))
  )
```

